---
title: 'Pantheon and The 2015 Census'
author:
- Joshua Levine
- Sebastian Whitworth
- Jared (the squid) Allmaras
runtime: shiny
output:
  html_document:
    theme: journal
    highlight: tango
    df_print: paged
    toc: yes
    toc_depth: '4'
  html_notebook:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include=FALSE}
library(tidyverse)
require(data.world)
library(shiny)
library(ggthemes)
knitr::opts_chunk$set(echo = TRUE)
```
  
## **R Session Info**  

```{r}
sessionInfo()
```

## **Github Link** 
https://github.com/stw436/testGit

## **Querying our data.world project** 
```{r}
project <- "https://data.world/stw436/f-17-edv-project-3"
data.world::set_config(cfg_env("DW_API"))
hpiByCountry <- data.world::query(data.world::qry_sql(
"SELECT UPPER(countryname) as countryName, hpi, continentname
FROM stw436.`pantheon-prj-4`.pantheon
WHERE continentname IS NOT NULL"
), dataset = project)
```

## **Introduction** 
Pantheon is an ambitious project from MIT Media Lab trying to help us understand the process of global cultural development. Simply, it is a dataset of famous people throughout history. It lists things like name, birthcity, occupation, domain, etc. But, the lynchpin here is the Human Popularity (hpi) which attempts to put a number on a persons "measure of cultural popularity." If you'd like to read about how they do that, [check this out](http://pantheon.media.mit.edu/methods)

In this project, we will combine this dataset with the US Census Bureau's 2015 census and build on our [previous analysis](https://jaredallmaras.shinyapps.io/PantheonProject/) in an attempt to make new insights.


## Getting Reacquainted With The Data
Comparing the mean HPI to the median HPI for the top 5 HPI countries by median
```{r }
# get the countries with the highest median
medianCountryHpi <- hpiByCountry %>% group_by(countryName) %>% mutate(Median = median(hpi))

countriesOrderedByMedian <- unique(medianCountryHpi$countryName [order (medianCountryHpi$Median, decreasing = TRUE)])[1 : 5]

topMedianCountry = subset (medianCountryHpi, countryName %in% countriesOrderedByMedian) 
topMedianCountry  = topMedianCountry[!duplicated(topMedianCountry['countryName']),]

# get the countries with the highest mean
meanCountryHpi <- hpiByCountry %>% group_by(countryName) %>% mutate(Mean = mean(hpi))

countriesOrderedByMean <- unique(meanCountryHpi$countryName [order (meanCountryHpi$Mean, decreasing = TRUE)])

topMeanCountryHpi <- subset (meanCountryHpi, countryName %in% countriesOrderedByMedian)
topMeanCountryHpi =
topMeanCountryHpi[!duplicated(topMeanCountryHpi['countryName']),]

# union topMeanCountryHpi and topMedianCountry
meanWithMedian = rbind(topMeanCountryHpi, topMedianCountry)
gatheredCombo = subset (gather(meanWithMedian, type, value, Mean:Median), value != "NA")

renderPlot({
  ggplot(gatheredCombo, 
       aes(x=countryName,
           y=value,
           color=type,
           shape=type)) + 
  geom_point(size = 10) + labs(x = "Country") +
  theme_wsj()
})
```
